Learning to Synthesize Rules for Rule-based Intrusion Detectors

### 2020-03-06 paper/paper.tex
pass 4.2

\textbf{Implementation details.} We implemented function
\emph{isPlausible} by 1)~updating Suricata to only monitor the rule
that is passed as parameter\Mar{isto realmente eh necessario? se sim,
  explique. me pareceu que o que vc. precisa ate aqui jah estaria no
  log do \suri}, 2)~replaying the negative benign traffic (see
Section~\ref{sec:dataset-benign}), and 3)~reading the Suricata logs to
check if any benign message was captured by the rule. \Mar{discuss
  filter function.} It is worth
noting that the benign traffic is stored in \emph{pcap}
files~\cite{pcap} and Suricata can process those files very
efficiently compared to analyzing network messages directly. Instead
of sending traffic to a machine with a deployed server (\eg{}, web
server) that \suri\ would monitor, our setup calls \suri\ directly
through an API. \suri\ is invoked multiple times in the process of
minimizing the rule.  \textbf{Limitations.} It is worth noting that
the performance of \tname{} depends on the quality of inputs. For the
positive malicious traffic, \tname{} only requires one sample (as
input to step one), but can benefit of several samples (see
line~\ref{filtering} of Algorithm~\ref{algo1}). The same applies to
the negative traffic. However, in this case, \tname{} can use a large
variety of public data sets available online (see
Section~\ref{sec:objectanalysis-benign}).

>>>>

\textbf{Implementation details.} We implemented function
\emph{isPlausible} by 1)~updating Suricata to only monitor the rule
that is passed as parameter\Mar{isto realmente eh necessario? se sim,
  explique. me pareceu que o que vc. precisa ate aqui jah estaria no
  log do \suri} \Luc{Nao precisa desse ponto. Para essa etapa foi preciso modificar o codigo do suricata para q ele fosse capaz de gerar mais de 15 alertas para um unico pacote. Durante a execução do Syrius pode ser gerada uma grande quantidade de regras q causam falsos positivos, eventualmente podem haver 15 delas q detectam erroneamente um mesmo pacote. Sem essa alteração, algumas regras q geram falso positivo n seriam eliminadas.}, 2)~replaying the negative benign traffic (see
Section~\ref{sec:dataset-benign}), and 3)~reading the Suricata logs to
check if any benign message was captured by the rule. \Mar{discuss
  filter function.} It is worth
noting that the benign traffic is stored in \emph{pcap}
files~\cite{pcap} and Suricata can process those files very
efficiently compared to analyzing network messages directly. Instead
of sending traffic to a machine with a deployed server (\eg{}, web
server) that \suri\ would monitor, our setup calls \suri\ directly
through an API. \suri\ is invoked multiple times in the process of
minimizing the rule.  \textbf{Limitations.} It is worth noting that
the performance of \tname{} depends on the quality of inputs. For the
positive malicious traffic, \tname{} only requires one sample (as
input to step one), but can benefit of several samples (see
line~\ref{filtering} of Algorithm~\ref{algo1}). The same applies to
the negative traffic. However, in this case, \tname{} can use a large
variety of public data sets available online (see
Section~\ref{sec:objectanalysis-benign}).
